---
title: "Density-dependence seedling mortality in Kadumane"
author: "Robert Bagchi and Ashwin Viswanathan"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  tufte::tufte_handout:
  number_sections: yes
toc: true
---
## set up

```{r load_packages}
library(tidyverse)
library(ggthemes)
library(knitr)

#library(vegan)
#library(grid)
#library(geosphere)
#library(mgcv)
library(glmmTMB)
library(DHARMa)
library(ggeffects)
library(sjPlot)
library(patchwork)
```

```{r graphic_setup}
theme_set(theme_tufte())
```

# Data 

Load data

```{r load_data}
sdls <- read_rds("data/kadumane_seedlings.rds")
site_dat <- read_rds("data/kadumane_site_metadata.rds")
plot_dat <- read_rds("data/kadumane_plot_metadata.rds")
```

1. Join in site and plot meta-data.

2. Remove rows for species with no seedlings at start of the census in plot.

3. Select species that 
* Are recorded in at least 5 plots.
* Vary in density among plots.
* Are groups of many (unidentified) species with the same code.

```{r select_species}
sdls <-  sdls |> left_join(site_dat) |> left_join(plot_dat) |> 
  filter(census.start > 0)

## find species with enough individuals and variation in density to allow 
## analysis
sp_list <- group_by(sdls, species) |> 
  summarise(n = sum(census.start > 0), ## number of plots withe species
            sd_dens = sd(census.start[census.start > 0])) |> ## variation in density 
  filter(n > 1) |> arrange(n)

## only lose 8 species by restricting to 5 or more occurrences (instead of 1)
## Seems reasonable. Also removing species that were unreliably identified.
## 
## @Ashwin - what was SC and Artoh?
sp_list <- filter(sp_list, n > 4, !(species %in% c("Palm", "Artoh", "SC")),
                  sd_dens > 0) 
sdls <- filter(sdls, species %in% sp_list$species)
dim(sdls) ## 968 columns

```

Rename columns, add total seedling density, scale and centre data.

```{r data_wrangling}
## shorten names
sdls <- rename(sdls, 
               "trt_F" = "treatment.fungicide", 
               "trt_I" = "treatment.insecticide", 
               "Pr_m" = "proportion.mortality",
               "gr" = "group",
               "loc" = "location")
                ## group causes problems with some helper funcs
## add total density
tot_dens <- sdls |> group_by(site, loc, gr, plot) |> 
  summarise(tot_dens = sum(census.start))

## add species mean density
## divide by total number of plots = 21 sites x 4 locs * 3 groups * 5 plots
sp_mean_dens <- sdls |> group_by(species) |> 
  summarise(sp_mean_dens = sum(census.start)/(21*4*3*5), 
            sp_mean_surv = sum(census.final)/sum(census.start)) 


sdls <- left_join(sdls, tot_dens, by = c("site", "loc", "gr", "plot")) |> 
  left_join(select(sp_mean_dens, - sp_mean_surv))

#scale density by mean, fix couple of NAs and calculate log density
sdls <- mutate(sdls, 
               slope.degrees = replace_na(slope.degrees, 5), 
               Pr_s = 1 - Pr_m,
               con_dens = census.start,
               con_dens_s = con_dens/sp_mean_dens,
               across(c(proportion.connectivity, slope.degrees),
                      ~as.vector(scale(.x)), .names = "{.col}_s"),
                trt_F = factor(trt_F, labels = c("0", "F")),
                trt_I = factor(trt_I, labels = c("0", "I"))
               )
dim(sdls) ## 968 species x plot combinations
sdls |> summarise(n_sdls = sum(census.start), 
                  n_survs = sum(census.final),
                  n_species = n_distinct(species)) |> knitr::kable()
```


# Models

## Raw conspecific density model

Fitting a model of mortality as a function of initial conspecific density, 
initial total density, biocide treatment and fragment area (and their
interactions).

Also including slope of plot and random intercepts for plot, nested in location,
nested in site. Random slopes and intercepts are included for each species to
examine how density dependence varies among species.

```{r fit_model}
# species random intercept and slope
m_cdd_ris <- glmmTMB(Pr_s ~ slope.degrees_s + 
                       (scale(tot_dens) + scale(con_dens)) * 
                       (trt_I + trt_F) *
                       scale(fragment.size) +
                       (scale(con_dens) + scale(tot_dens)||species) +
                       ## setting cor to 0 to converge 
                       (1|site/loc/gr/plot), 
                     weights = census.start, data = sdls, 
                     family=binomial)
## species random intercept model
m_cdd_ri <- glmmTMB(Pr_s ~ slope.degrees_s + 
                      (scale(tot_dens) + scale(con_dens)) * 
                      (trt_I + trt_F) *
                      scale(fragment.size) +
                      (1|species) +
                      (1|site/loc/gr/plot), 
                    weights = census.start, data = sdls, 
                    family=binomial)
# species random intercept and slope
m_logcdd_ris <- glmmTMB(Pr_s ~ slope.degrees_s + 
                   (scale(log(tot_dens)) + scale(log(con_dens))) * 
                      (trt_I + trt_F) *  scale(fragment.size) +
                   (scale(log(con_dens)) + scale(log(tot_dens))||species) +  
                   (1|site/loc/gr/plot), 
                 weights = census.start, data = sdls, 
                 family=binomial)
# species random intercept only
m_logcdd_ri <- glmmTMB(Pr_s ~ slope.degrees_s + 
                   (scale(log(tot_dens)) + scale(log(con_dens))) * 
                      (trt_I + trt_F) *  scale(fragment.size) +
                   (1|species) +  
                   (1|site/loc/gr/plot), 
                 weights = census.start, data = sdls, 
                 family=binomial)
AIC(m_cdd_ris, m_cdd_ri, m_logcdd_ris, m_logcdd_ri)
## non-logged version a bit better.
```

Note that including the insecticide x fungicide interaction causes convergence
problems and doesn't seem to be important either. Removing for practicality.

### Scaled conspecific density models

The most abundant species initially will often have lower survival (fecundity/
survival trade-off). This could generate what looks like a density-dependent 
relationship when looking across species, even without a relationship 
within species (i.e., Simpson's paradox). 
```{r abundance_survival}

ggplot(sp_mean_dens, aes(x = log(sp_mean_dens), y = sp_mean_surv)) +
  geom_label(aes(label= species)) + geom_smooth(method = "lm") + theme_tufte()
#  scale_x_continuous(trans = "log")
## not the clearest pattern, but worth accounting for.

(ggplot(sdls, aes(x = scale(log(con_dens_s)), colour = species)) + geom_density())/
(ggplot(sdls, aes(x = scale(log(con_dens)), colour = species)) + geom_density()) + plot_layout(guides = "collect")

```



To account for this, we can scale conspecific density by dividing by mean
density and refitting the models.

```{r fit_scaled_models}
## models using scaled density
m_cdd_s_ris <- glmmTMB(Pr_s ~ slope.degrees_s + 
                       (scale(tot_dens) + scale(con_dens_s)) * 
                       (trt_I + trt_F) *
                       scale(fragment.size) +
                       (scale(con_dens_s) + scale(tot_dens)||species) +
                       ## setting cor to 0 to converge 
                       (1|site/loc/gr/plot), 
                     weights = census.start, data = sdls, 
                     family=binomial)

m_logcdd_s_ris <- glmmTMB(Pr_s ~ slope.degrees_s + 
                       (scale(log(tot_dens)) + scale(log(con_dens_s))) * 
                       (trt_I + trt_F) *
                       scale(fragment.size) +
                       (scale(log(con_dens_s)) + scale(log(tot_dens))||species) +
                       ## setting cor to 0 to converge 
                       (1|site/loc/gr/plot), 
                     weights = census.start, data = sdls, 
                     family=binomial)

AIC(m_logcdd_s_ris, m_cdd_s_ris) ## comparable.
```

##  Model diagnostics

```{r diagnostics}
## no evidence of variation among species
res <- simulateResiduals(m_cdd_ri)
plot(res)
res_log <- simulateResiduals(m_logcdd_ri)
plot(res_log) ## slightly less convincing, but acceptable


## look at relationship with covariates
diag_dat <- data.frame(m_cdd_ri$frame, res = res$fittedResiduals)

diag_dat <-   rename_with(diag_dat, ~ str_replace(.x, "scale\\.", "")) |> 
  rename_with(~str_replace(.x, "\\.$", "")) 

ggplot(diag_dat, aes(x = con_dens, y = res)) +  
  geom_point(aes(colour = species)) + 
  geom_hline(yintercept=0, linetype = "dashed") +
  geom_smooth(method="gam") ## no clear trend. 

ggplot(diag_dat, aes(x = fragment.size, y = res)) +  
  geom_point(aes(colour = species), position = "jitter") + 
  geom_hline(yintercept=0, linetype = "dashed") +
  geom_smooth(method="gam") ## no clear trend. 


ggplot(diag_dat, aes(x = con_dens, y = res)) +  
  facet_wrap(~trt_F + trt_I ) +
  geom_point(aes(colour = species)) +
  geom_smooth(method="gam") ## no trend with treatment


diag_datlog <- data.frame(m_logcdd_ri$frame, res = res_log$fittedResiduals)
diag_datlog <-   rename_with(diag_datlog, ~ str_replace(.x, "scale\\.", "")) |> 
  rename_with(~str_replace(.x, "\\.$", "")) |> 
  rename_with(~str_replace(.x, "\\.$", ""))
names(diag_datlog)

ggplot(diag_datlog, aes(x = log.con_dens, y = res)) +  
  geom_point(aes(colour = species)) + 
  geom_hline(yintercept=0, linetype = "dashed") +
  geom_smooth(method="gam") ## slight trend. 


ggplot(diag_datlog, aes(x = log.con_dens, y = res, colour = trt_F)) + 
  facet_wrap(~species) +
  geom_point() + geom_smooth(method="gam") ## no indication of a problem


```

## Take-homes

* Model diagnostics are generally good.
* Lower AIC for log density version. 
* Diagnostics are slightly better for non-logged version. Logged version has
some evidence of quantiles deviating from expectations. 
* No evidence of trends between covariates and residuals. 

The log density model has a slightly lower AIC. A little poking around 
(not shown) suggests that excluding the largest values reverses this order, 
so that the non-logged version is better. 

Looks like the two models lead to roughly similar interpretation (below).

```{r diag_scaled}
res_s <- simulateResiduals(m_cdd_s_ris)
plot(res_s) ## ok - some deviation from ideal residual distribution
res_log_s <- simulateResiduals(m_logcdd_s_ris)
plot(res_log_s) ## not as good.


## look at relationship with covariates
diag_dat <- data.frame(m_cdd_s_ris$frame, res = res_s$fittedResiduals)

diag_dat <-   rename_with(diag_dat, ~ str_replace(.x, "scale\\.", "")) |> 
  rename_with(~str_replace(.x, "\\.$", "")) 

ggplot(diag_dat, aes(x = con_dens_s, y = res)) +  
  geom_point(aes(colour = species)) + 
  geom_hline(yintercept=0, linetype = "dashed") +
  geom_smooth(method="gam") ## no clear trend. 

ggplot(diag_dat, aes(x = fragment.size, y = res)) +  
  geom_point(aes(colour = species), position = "jitter") + 
  geom_hline(yintercept=0, linetype = "dashed") +
  geom_smooth(method="gam") ## no clear trend. 

ggplot(diag_dat, aes(x = con_dens_s, y = res)) +  
  facet_wrap(~trt_F + trt_I ) +
  geom_point(aes(colour = species)) +
  geom_smooth(method="gam") ## no trend with treatment

## Logged version
## 
diag_dat <- data.frame(m_logcdd_s_ris$frame, res = res_log_s$fittedResiduals)

diag_dat <-   rename_with(diag_dat, ~ str_replace(.x, "scale\\.", "")) |> 
  rename_with(~str_replace(.x, "\\.$", "")) 

ggplot(diag_dat, aes(x = log.con_dens_s., y = res)) +  
  geom_point(aes(colour = species)) + 
  geom_hline(yintercept=0, linetype = "dashed") +
  geom_smooth(method="gam") ## bit of a trend 

ggplot(diag_dat, aes(x = fragment.size, y = res)) +  
  geom_point(aes(colour = species), position = "jitter") + 
  geom_hline(yintercept=0, linetype = "dashed") +
  geom_smooth(method="gam") ## no clear trend. 

ggplot(diag_dat, aes(x = log.con_dens_s., y = res)) +  
  facet_wrap(~trt_F + trt_I ) +
  geom_point(aes(colour = species)) +
  geom_smooth(method="gam") ## bit of a trend in control and both 
# biocides treatments

```

The diagnostics aren't as perfect in the scaled case, but the scaled version
does seem to be sensible given the massive differences in density.

## Model inference

### Non-scaled model 

The fixed effects

```{r inference}
## Non-logged version
summary(m_cdd_ri)
terms_cdd <- names(fixef(m_cdd_ri)$cond)

#sjPlot::plot_model(m_cdd) ## bit busy
trt_cols <- terms_cdd[-c(1:2)]
trt_cols <- trt_cols[!str_detect(trt_cols, "tot")] 
trt_cols <- case_when(
  str_detect(trt_cols, "trt_II") ~ "Insecticide",
  str_detect(trt_cols, "trt_FF") ~ "Fungicide",
  .default = "Control")
            
tp_cdd_ri <- sjPlot::plot_model(m_cdd_ri, 
                    rm.terms = c("slope.degrees_s", 
                                 terms_cdd[str_detect(terms_cdd, "tot")]),
                   group.terms= trt_cols, colors="Set2", title=NA)


quantile(sdls$con_dens, seq(0, 1, 0.1))
quantile(site_dat$fragment.size, seq(0, 1, 0.1))
plot(ggpredict(m_cdd_ri, terms=c("con_dens[1:100, by=0.1]", 
                              "trt_F",
                              "fragment.size[1, 50, 100]"))) + theme_tufte()

## Logged version

summary(m_logcdd_ri)
                                     
terms_logcdd <- names(fixef(m_logcdd_ri)$cond)
sjPlot::plot_model(m_logcdd_ri, 
                   rm.terms = c("slope.degrees_s", 
                                terms_logcdd[str_detect(terms_logcdd, "tot")]),
                   group.terms= trt_cols, colors="Set2")

plot(ggpredict(m_logcdd_ri, terms=c("con_dens[1:100, by = 1]", 
                              "trt_F",
                              "fragment.size[1, 50, 100]"))) + theme_tufte()
p_cdd_ri <- predict_response(m_cdd_ri, 
                                terms=c("con_dens[1:100, by = 1]", 
                                        "trt_F", "trt_I", 
                                        "fragment.size[1, 50, 100]"),
                             margin="marginalmeans")

pr_cdd_ri <- residualize_over_grid(p_cdd_ri, m_cdd_ri) |> 
   bind_cols(species = sdls$species) |> 
  mutate(trt = case_when(
    group == "0" & facet == "0" ~ "C",
    group == "F" & facet == "0" ~ "F",
    group == "0" & facet == "I" ~ "I",
    group == "F" & facet == "I" ~ "FI"), 
    facet_lab = "Fragment Area (ha)") |> 
  rename("con_dens" = "x", "frag_area" = "panel") |> 
  group_by(con_dens, trt, frag_area, facet_lab, species) |> 
  summarise(predicted = mean(predicted), n = n())

p_cdd_ri <- as.data.frame(p_cdd_ri) |> 
  mutate(trt = case_when(
    group == "0" & facet == "0" ~ "C",
    group == "F" & facet == "0" ~ "F",
    group == "0" & facet == "I" ~ "I",
    group == "F" & facet == "I" ~ "FI"), 
    facet_lab = "Fragment Area (ha)") |> 
  rename("con_dens" = "x", "frag_area" = "panel")

pl_cdd <- ggplot(filter(p_cdd_ri, trt !="FI"), 
       aes(x=con_dens, y = predicted, colour = trt)) +
  ggh4x::facet_nested(~facet_lab + frag_area) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = trt), 
              colour = NA, alpha = 0.3) + 
  geom_line() +
  geom_point(data = filter(pr_cdd_ri, trt != "FI")) +
  scale_colour_brewer(palette="Set2") + 
  scale_fill_brewer(palette="Set2") +
  labs(x = expression(Conspecific~density~(m^-2)), y = "Pr(Survival)", 
       colour = "Treatment", fill = "Treatment")
pl_cdd
tp_cdd_ri
```

Main conclusions
* Suppressing insects and fungi) increases survival. 
* Conspecific density reduces seedling survival.
* The protection by fungicide is less effective at high conspecific density
* There is a weak 3-way interaction between conspecific density, fragment size, 
and fungicide addition, so that the reduction in protection at high densities
is more evident in larger fragments.

### Scaled model 

```{r inference_scaled}
## Non-logged version
summary(m_cdd_s_ris)
plot_model(m_cdd_s_ris, show.values=TRUE )

## obvious effects of conspeicfic density. Less clear effect of 
## fungicide x condens. But perhaps that is partly due to interactions. 
## Examining a simpler model (no 3-way interactions)
summary(update(m_cdd_s_ris, ~.-(trt_F + trt_I):scale(fragment.size):
                 (scale(con_dens_s) + scale(tot_dens))))
plot_model(update(m_cdd_s_ris, ~.-(trt_F + trt_I):scale(fragment.size):
                 (scale(con_dens_s) + scale(tot_dens))))
## There is a tendency for fungicide to have a bigger effect in large
## fragments. Examine effects when split up by fragment size

## models using scaled density

m_cdd_s_ris_frag <- lapply(split(sdls, 
                                 f= cut(sdls$fragment.size, 
                                        quantile(site_dat$fragment.size, 
                                                 c(0, 0.25, 0.5, 0.75, 1)), 
                                        include.lowest=TRUE)), 
                           function(d){
                             glmmTMB(Pr_s ~ slope.degrees_s + 
                                       (scale(tot_dens) + scale(con_dens_s)) * 
                                       (trt_I + trt_F) +
                                       (scale(con_dens_s) + 
                                          scale(tot_dens)||species) +
                                       ## setting cor to 0 to converge 
                                       (1|site/loc/gr/plot), 
                                     weights = census.start, data = d, 
                                     family=binomial)})

plot_models(m_cdd_s_ris_frag, show.values=TRUE, 
            m.labels=names(m_cdd_s_ris_frag))
lapply(m_cdd_s_ris_frag, summary)

```

```{r plots}
terms_cdd <- names(fixef(m_cdd_s_ris)$cond)
#sjPlot::plot_model(m_cdd) ## bit busy
trt_cols <- terms_cdd[-c(1:2)]
trt_cols <- trt_cols[!str_detect(trt_cols, "tot")] 
trt_cols <- case_when(
  str_detect(trt_cols, "trt_II") ~  "Insecticide",
  str_detect(trt_cols, "trt_FF") ~ "Fungicide",
  .default =  "Control")

labs <-  c("ConDens", "I", "F", "FragArea",
              "ConDens x I", "ConDens x F", "FragArea x\n ConDens",
              "FragArea x I"  , "FragArea x F", 
              "FragArea x\n(ConDens x I)", 
              "FragArea x\n(ConDens x F)")

tp_cdd_s_ris <- 
    sjPlot::plot_model(m_cdd_s_ris, 
                       rm.terms = c("slope.degrees_s", 
                                    terms_cdd[str_detect(terms_cdd, "tot")]),
                       group.terms= trt_cols)

tp_cdd_s_ris <- tp_cdd_s_ris$data   |> 
  mutate(term = factor(labs, levels = rev(labs))) |> 
  ggplot(aes(y = term, x = estimate, xmin = conf.low, xmax = conf.high, 
             colour = group)) + 
  geom_pointrange() +
  geom_vline(xintercept=1, linetype = "dotted") +
  scale_colour_brewer(palette="Set2", name="Treatment") +
  labs(y = NULL, x = "Odds ratio")  + 
  guides(colour = guide_legend(position = "top", direction = "horizontal", 
                               title.position = "top", title.hjust = 0.5)) +
  theme(
    legend.margin = margin(0, 0, 0, 0), 
    legend.justification.top = "left",
    legend.location = "plot",
    plot.title.position = "plot"
  )                                        
  
tp_cdd_s_ris 

quantile(sdls$con_dens_s, seq(0, 1, 0.1))
quantile(site_dat$fragment.size, seq(0, 1, 0.1))
plot(ggpredict(m_cdd_s_ris, terms=c("con_dens_s[1:80, by=0.1]", 
                              "trt_F",
                              "fragment.size[1, 50, 100]"))) + theme_tufte()

## Logged version

summary(m_logcdd_s_ris)
                                     
terms_logcdd <- names(fixef(m_logcdd_s_ris)$cond)
sjPlot::plot_model(m_logcdd_s_ris, 
                   rm.terms = c("slope.degrees_s", 
                                terms_logcdd[str_detect(terms_logcdd, "tot")]),
                   group.terms= trt_cols, colors="Set2")

plot(ggpredict(m_logcdd_s_ris, terms=c("con_dens_s[1:80, by = 1]", 
                              "trt_F",  
                              "fragment.size[1, 50, 100]"))) + theme_tufte()

## given that the diagnostics were better for the untransformed scale
## model, using that for a more comprehensive plot

p_cdd_s_ris <- predict_response(m_cdd_s_ris, 
                                terms=c("con_dens_s[1:80, by = 1]", 
                                        "trt_F", "trt_I", 
                                        "fragment.size[2, 100]"),
                             margin="marginalmeans")

pr_cdd_s_ris <- residualize_over_grid(p_cdd_s_ris, m_cdd_s_ris) |> 
   bind_cols(species = sdls$species) |> 
  mutate(trt = case_when(
    group == "0" & facet == "0" ~ "Control",
    group == "F" & facet == "0" ~ "Fungicide",
    group == "0" & facet == "I" ~ "Insecticide",
    group == "F" & facet == "I" ~ "FI"), 
    facet_lab = "Fragment Area (ha)") |> 
  rename("con_dens" = "x", "frag_area" = "panel") |> 
  group_by(con_dens, trt, frag_area, facet_lab, species) |> 
  summarise(predicted = mean(predicted), n = n())

p_cdd_s_ris <- as.data.frame(p_cdd_s_ris) |> 
  mutate(trt = case_when(
    group == "0" & facet == "0" ~ "Control",
    group == "F" & facet == "0" ~ "Fungicide",
    group == "0" & facet == "I" ~ "Insecticide",
    group == "F" & facet == "I" ~ "FI"), 
    facet_lab = "Fragment Area (ha)") |> 
  rename("con_dens" = "x", "frag_area" = "panel")

pl_cdd_s <- ggplot(filter(p_cdd_s_ris, trt !="FI"), 
       aes(x=con_dens, y = predicted, colour = trt)) +
  ggh4x::facet_nested(~facet_lab + frag_area) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = trt), 
              colour = NA, alpha = 0.3) + 
  geom_line() +
  geom_point(data = filter(pr_cdd_s_ris, trt != "FI")) +
  scale_colour_brewer(palette="Set2") + 
  scale_fill_brewer(palette="Set2", guide = "none") +
  labs(x = expression(Conspecific~density~(m^-2)), y = "Pr(Survival)", 
       colour = "Treatment") + theme(legend.position="none")


(pl_cdd_s  | tp_cdd_s_ris )  + 
  plot_layout(widths=c(0.6, 0.4))

```

Main take-aways

* Survival is negatively affected by Conspecific density.
* Insecticide increases survival, fungicide doesn't make an appreciable 
difference.


## Species specific inferences.

Initial analyses suggested that some species were heavily influencing the results. 
The random slope should partly account for that.

```{r species_effects}
sjPlot::plot_model(m_cdd_ris, type = "re", terms = "species", ri.nr = 1)
## very little variation among species in slopes
sp_eff <- as.data.frame(ranef(m_cdd_ris, condVar = T)$cond$species)

sp_eff <- bind_cols(sp_eff, 
                    t(apply(attr(sp_eff, "condVar"), 3, function(x) sqrt(diag(x)))))
names(sp_eff) <- c("Intercept", "con_dens", "tot_dens", 
                   "Intercept_se", "con_dens_se", "tot_dens_se")
sp_eff <- mutate(sp_eff, sp_names = row.names(sp_eff))

sp_eff |> arrange(con_dens) |> 
  ggplot(aes(y = sp_names, x = con_dens, 
             xmin = con_dens - 2*con_dens_se, 
             xmax = con_dens + 2*con_dens_se)) +
    geom_vline(xintercept=0, linetype = "dotted") +
  geom_pointrange() 
## nothing going on. Basically all 0. 

sp_eff |> arrange(Intercept) |> 
  mutate(sp_names = factor(1:nrow(sp_eff), labels = sp_names)) |> 
  ggplot(aes(y = sp_names, x = Intercept, 
             xmin = Intercept - 2*Intercept_se, 
             xmax = Intercept + 2*Intercept_se)) +
  geom_vline(xintercept=0, linetype = "dotted") +
  geom_pointrange()  

```


Almost no variation in cdd among species. 


Perhaps remove most abundant species to check if patterns are robust.

```{r species_influence}
sp_common <- sdls |> group_by(species) |> summarise(n = sum(census.start)) |> 
   arrange(desc(n)) |> pull(species)
sp_mods <- lapply(c("none", as.character(sp_common[1:4])), function(i) {
  update(m_cdd_ri, data = filter(sdls, !species == i))})


library(sjPlot)

plot_models(sp_mods,
            rm.terms = c("slope.degrees_s", 
                         terms_cdd[str_detect(terms_cdd, "tot")]),
            m.labels = c("None", as.character(sp_common[1:4])))

## Only species that makes a difference is S. rubicundum. 
summary(sp_mods[[2]]) ## still significant effects of conspecific density,
# and insecticide and fungicide, and interaction between density and fungicide.

```

### scaled versions

```{r species_influence}
sp_common <- sdls |> group_by(species) |> summarise(n = sum(census.start)) |> 
   arrange(desc(n)) |> pull(species)
sp_mods <- lapply(c("none", as.character(sp_common[1:5])), function(i) {
  update(m_cdd_s_ris, data = filter(sdls, !species == i))})

sjPlot::plot_models(sp_mods,
            rm.terms = c("slope.degrees_s", 
                         terms_cdd[str_detect(terms_cdd, "tot")]),
            m.labels = c("None", as.character(sp_common[1:5])))

## No species seems to make a bit difference
summary(sp_mods[[2]]) ## still significant effects of conspecific density,
# and insecticide and fungicide, and interaction between density and fungicide.

```




what about single species models?
```{r single_sp}
## base model
m_cdd_1sp <- update(m_cdd_ri, ~.-(1|species))  ## remove species random effect
summary(m_cdd_1sp) ## check

single_sp_mods <- lapply(sp_common[1:6], function(i) {
  update(m_cdd_1sp, data = filter(sdls, species == i))})

sr_dat <- filter(sdls, species == "SR") |> droplevels()

m_sr <- glmmTMB(Pr_m ~ (scale(con_dens) + scale(tot_dens)) *
                  (trt_F + trt_I) *  scale(fragment.size) +
                  (1|site/loc/gr/plot), weights = census.start, 
                family = binomial, data = sr_dat)

m_srb <- glmmTMB(Pr_m ~ (scale(con_dens) ) *
                  (trt_F + trt_I) *  scale(fragment.size) +
                  (1|site/loc/gr/plot), weights = census.start, 
                family = binomial, data = sr_dat)
summary(m_sr)

plot_models(single_sp_mods[1:5], std.est = "std", 
            rm.terms = c("slope.degrees_s", 
                         terms_cdd[str_detect(terms_cdd, "tot")]),
            m.labels =  sp_common[1:5], grid = TRUE)

```

```{r oldcode, eval = FALSE, include = FALSE}



temp$statusm = scale(temp$census.start, center = F)
temp$sizem = scale(temp$fragment.size, center = F)

temp$logdensm = scale(temp$logdens)
temp[is.na(temp$slope.degrees),]$slope.degrees = 5 
temp$slope.degrees = temp$slope.degrees/100
temp$slope.degrees = scale(temp$slope.degrees, center = F)


temp = temp[temp$census.start != 49,]
temp = temp[temp$species != "Symp" | temp$plot != "5" | temp$census.start != 15,]


temp$plotx = temp$plot
temp[temp$plotx == "2",]$plotx = "1"

mat = rbind(c(-0.5,0.5))
#library(MASS)
cMat = MASS::ginv(mat)

temp1 = temp

fit9a = glmer (proportion.mortality ~ treatment.fungicide * 
                 treatment.insecticide*statusm + 
                 treatment.fungicide*treatment.insecticide*sizem +
                 slope.degrees + (1|species) + (0 + statusm|species) +
                 (1|location.code/group/plot), 
               weights = census.start, data = temp1, 
               contrasts = list(treatment.fungicide = cMat,
                                treatment.insecticide = cMat), 
               family="binomial", nAGQ = 1)

sum(resid(fit9a, type = "pearson")^2)
df.residual(fit9a)
library(glmmTMB)
fit <- glmmTMB (proportion.mortality ~ treatment.fungicide * 
                 treatment.insecticide*statusm + 
                 treatment.fungicide*treatment.insecticide*sizem +
                 slope.degrees + (1|species) + (0 + statusm|species) +
                 (1|location.code/group/plot), 
               weights = census.start, data = temp1, 
               contrasts = list(treatment.fungicide = cMat,
                                treatment.insecticide = cMat), 
               family=binomial)
summary(fit)
plot(ranef(fit)$cond$species$statusm)

# SR

temp = seedling_census_data[seedling_census_data$census.start >= 1 & seedling_census_data$species == "SR" & seedling_census_data$census.start <= 300,]
#temp[temp$plot == "6",]$treatment.fungicide = 2
temp$treatment.fungicide = as.factor(temp$treatment.fungicide)
#temp[temp$plot == "5",]$treatment.insecticide = 2
temp$treatment.insecticide = as.factor(temp$treatment.insecticide)
temp$statusm = scale(temp$census.start, center = F)
temp$sizem = scale(temp$fragment.size, center = F)
temp$logdens = log(temp$census.start)
temp$logdensm = scale(temp$logdens)
#temp[is.na(temp$slope.degrees),]$slope.degrees = 5 
temp$slope.degrees = temp$slope.degrees/100
temp$slope.degrees = scale(temp$slope.degrees, center = F)
temp = temp[-c(142,49),]

temp$plotx = temp$plot
temp[temp$plotx == "2",]$plotx = "1"

mat = rbind(c(-0.5,0.5))
library(MASS)
cMat = ginv(mat)

temp2 = temp

fit9b = glmer (proportion.mortality ~ treatment.fungicide*treatment.insecticide*statusm + treatment.fungicide*treatment.insecticide*sizem + slope.degrees + 
                 (1|location.code/group/plot), weights = census.start, data = temp2, 
               contrasts = list(treatment.fungicide = cMat,treatment.insecticide = cMat), family="binomial", nAGQ = 0)





# SP


temp = seedling_census_data[seedling_census_data$census.start >= 1 & seedling_census_data$species == "Climber1",]
#temp[temp$plot == "6",]$treatment.fungicide = 2
temp$treatment.fungicide = as.factor(temp$treatment.fungicide)
#temp[temp$plot == "5",]$treatment.insecticide = 2
temp$treatment.insecticide = as.factor(temp$treatment.insecticide)
temp$statusm = scale(temp$census.start, center = F)
temp$sizem = scale(temp$fragment.size, center = F)
temp$logdens = log(temp$census.start)
temp$logdensm = scale(temp$logdens)
#temp[is.na(temp$slope.degrees),]$slope.degrees = 5 
temp$slope.degrees = temp$slope.degrees/100
temp$slope.degrees = scale(temp$slope.degrees, center = F)
temp = temp[temp$census.start != 49,]

temp$plotx = temp$plot
temp[temp$plotx == "2",]$plotx = "1"


mat = rbind(c(-0.5,0.5))
library(MASS)
cMat = ginv(mat)

temp3 = temp

fit9c = glmer (proportion.mortality ~ treatment.fungicide*treatment.insecticide*statusm + slope.degrees + 
                 (1|group.code/plot), weights = census.start, data = temp3,
               contrasts = list(treatment.fungicide = cMat,treatment.insecticide = cMat), family="binomial", nAGQ = 0)





# Symp

temp = seedling_census_data[seedling_census_data$census.start >= 1 & seedling_census_data$species == "Symp",]
#temp[temp$plot == "6",]$treatment.fungicide = 2
temp$treatment.fungicide = as.factor(temp$treatment.fungicide)
#temp[temp$plot == "5",]$treatment.insecticide = 2
temp$treatment.insecticide = as.factor(temp$treatment.insecticide)
temp$statusm = scale(temp$census.start, center = F)
temp$sizem = scale(temp$fragment.size, center = F)
temp$logdens = log(temp$census.start)
temp$logdensm = scale(temp$logdens)
temp[is.na(temp$slope.degrees),]$slope.degrees = 5 
temp$slope.degrees = temp$slope.degrees/100
temp$slope.degrees = scale(temp$slope.degrees, center = F)
temp = temp[temp$species != "Symp" | temp$plot != "5" | temp$census.start != 15,]

temp$plotx = temp$plot
temp[temp$plotx == "2",]$plotx = "1"

mat = rbind(c(-0.5,0.5))
library(MASS)
cMat = ginv(mat)

temp4 = temp

fit9d = glmer (proportion.mortality ~ treatment.fungicide*treatment.insecticide*statusm + slope.degrees +
                 (1|location.code/group/plot), weights = census.start, data = temp4,
               contrasts = list(treatment.fungicide = cMat, treatment.insecticide = cMat), family="binomial", nAGQ = 0)






# VM

temp = seedling_census_data[seedling_census_data$census.start >= 1 & seedling_census_data$species == "FLC",]
temp = temp[temp$census.start < 60,]

#temp[temp$plot == "6",]$treatment.fungicide = 2
temp$treatment.fungicide = as.factor(temp$treatment.fungicide)
#temp[temp$plot == "5",]$treatment.insecticide = 2
temp$treatment.insecticide = as.factor(temp$treatment.insecticide)
temp$statusm = scale(temp$census.start, center = F)
temp$sizem = scale(temp$fragment.size, center = F)
temp$logdens = log(temp$census.start)
temp$logdensm = scale(temp$logdens)
#temp[is.na(temp$slope.degrees),]$slope.degrees = 5 
temp$slope.degrees = temp$slope.degrees/100
temp$slope.degrees = scale(temp$slope.degrees, center = F)

temp$plotx = temp$plot
temp[temp$plotx == "2",]$plotx = "1"

mat = rbind(c(-0.5,0.5))
library(MASS)
cMat = ginv(mat)

temp5 = temp

fit9e = glmer (proportion.mortality ~ treatment.fungicide*treatment.insecticide + statusm + slope.degrees + (1|location.code/group),
               weights = census.start, data = temp5, contrasts = list(treatment.fungicide = cMat, treatment.insecticide = cMat),
               family="binomial", nAGQ = 0)





# all others

y = table(seedling_census_data[seedling_census_data$census.start != 0,]$species)
y = y[y>=5]

temp = seedling_census_data[seedling_census_data$census.start >= 1 & seedling_census_data$species != "SR" & seedling_census_data$species != "Symp" & 
                 seedling_census_data$species != "Climber1" & seedling_census_data$species != "SC" & seedling_census_data$species %in% names(y),]
temp = temp[temp$species != "Hopea" & temp$species != "Artoh" & temp$species != "Palm",]
temp = temp[temp$species != "FLC",]

#temp[temp$plot == "6",]$treatment.fungicide = 2
temp$treatment.fungicide = as.factor(temp$treatment.fungicide)
#temp[temp$plot == "5",]$treatment.insecticide = 2
temp$treatment.insecticide = as.factor(temp$treatment.insecticide)
temp$statusm = scale(temp$census.start, center = F)
#temp$AOm = scale(temp$AO, center = F)
temp$sizem = scale(temp$fragment.size, center = F)
temp$logdens = log(temp$census.start)
temp$logdensm = scale(temp$logdens)
temp[is.na(temp$slope.degrees),]$slope.degrees = 5 
temp$slope.degrees = temp$slope.degrees/100
temp$slope.degrees = scale(temp$slope.degrees, center = F)

temp$plotx = temp$plot
temp[temp$plotx == "2",]$plotx = "1"

mat = rbind(c(-0.5,0.5))
library(MASS)
cMat = ginv(mat)

temp6 = temp

fit9f = glmer (proportion.mortality ~ treatment.fungicide*treatment.insecticide*statusm + treatment.fungicide*treatment.insecticide*sizem + slope.degrees + (1|species) + (0 + statusm|species) +
                 (1|location.code/group/plot), weights = census.start, data = temp6,
               contrasts = list(treatment.fungicide = cMat,treatment.insecticide = cMat), family="binomial", nAGQ = 0)





##################### plotting - all species ######################



temp1$pred = predict(fit9a, type = "response", re.form = NA, allow.new.levels=TRUE)

a = predict(fit9a, type = "response", re.form = NA)
b = predict(fit9a, type = "response")
c = b - a
temp1$newproportion.mortality = temp1$proportion.mortality - c
temp1[temp1$newproportion.mortality > 1,]$newproportion.mortality = 1
temp1[temp1$newproportion.mortality < 0,]$newproportion.mortality = 0

temp1$predm = 0
temp1$sel = 0
temp1$ser = 0


ltemp = temp1

predFun = function(fit) {
  predict(fit,ltemp, re.form = NA, allow.new.levels=TRUE)
}

bb = bootMer(fit9a,nsim=100,FUN=predFun)

for (i in 1:length(temp1$proportion.mortality))
{
  temp1$predm[i] = binomial()$linkinv(median(bb$t[,i]))
  temp1$sel[i] = binomial()$linkinv(median(bb$t[,i]) - sd(bb$t[,i]))
  temp1$ser[i] = binomial()$linkinv(median(bb$t[,i]) + sd(bb$t[,i]))
}

ggp = ggplot(temp1, aes(x = census.start, y = predm, col = as.factor(plotx)))  +
  geom_point(size = 2) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F) +
  geom_smooth(aes(x = census.start, y = sel, col = as.factor(plotx)), method = "glm", method.args = list(family = "binomial"), se = F) +
  
  geom_smooth(aes(x = census.start, y = ser, col = as.factor(plotx)), method = "glm", method.args = list(family = "binomial"), se = F)

##### 1

selribx = ggplot_build(ggp)$data[[3]]$x[1:80]
selriby = ggplot_build(ggp)$data[[3]]$y[1:80]

serribx = ggplot_build(ggp)$data[[4]]$x[1:80]
serriby = ggplot_build(ggp)$data[[4]]$y[1:80]

srib = cbind(selribx,selriby,serriby)
srib = as.data.frame(srib)

srib = srib[sample(nrow(srib),length(temp1[temp1$treatment.control == 1,]$proportion.mortality),replace = T),]
temp1$selribx[temp1$treatment.control == 1] = srib$selribx
temp1$selriby[temp1$treatment.control == 1] = srib$selriby
temp1$serriby[temp1$treatment.control == 1] = srib$serriby

##### 2

selribx = ggplot_build(ggp)$data[[3]]$x[81:160]
selriby = ggplot_build(ggp)$data[[3]]$y[81:160]

serribx = ggplot_build(ggp)$data[[4]]$x[81:160]
serriby = ggplot_build(ggp)$data[[4]]$y[81:160]

srib = cbind(selribx,selriby,serriby)
srib = as.data.frame(srib)

srib = srib[sample(nrow(srib),length(temp1[temp1$plot == "5",]$proportion.mortality),replace = T),]
temp1$selribx[temp1$plot == "5"] = srib$selribx
temp1$selriby[temp1$plot == "5"] = srib$selriby
temp1$serriby[temp1$plot == "5"] = srib$serriby

##### 3

selribx = ggplot_build(ggp)$data[[3]]$x[161:240]
selriby = ggplot_build(ggp)$data[[3]]$y[161:240]

serribx = ggplot_build(ggp)$data[[4]]$x[161:240]
serriby = ggplot_build(ggp)$data[[4]]$y[161:240]

srib = cbind(selribx,selriby,serriby)
srib = as.data.frame(srib)

srib = srib[sample(nrow(srib),length(temp1[temp1$plot == "6",]$proportion.mortality),replace = T),]
temp1$selribx[temp1$plot == "6"] = srib$selribx
temp1$selriby[temp1$plot == "6"] = srib$selriby
temp1$serriby[temp1$plot == "6"] = srib$serriby

##### 4

selribx = ggplot_build(ggp)$data[[3]]$x[241:320]
selriby = ggplot_build(ggp)$data[[3]]$y[241:320]

serribx = ggplot_build(ggp)$data[[4]]$x[241:320]
serriby = ggplot_build(ggp)$data[[4]]$y[241:320]

srib = cbind(selribx,selriby,serriby)
srib = as.data.frame(srib)

srib = srib[sample(nrow(srib),length(temp1[temp1$plot == "7",]$proportion.mortality),replace = T),]
temp1$selribx[temp1$plot == "7"] = srib$selribx
temp1$selriby[temp1$plot == "7"] = srib$selriby
temp1$serriby[temp1$plot == "7"] = srib$serriby



ggp = ggplot(temp1, aes(x = census.start, y = predm, col = as.factor(plotx), fill = as.factor(plotx)))  +
  geom_point(aes(x = census.start, y = newproportion.mortality, col = as.factor(plotx)), size = 0.5) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, linewidth = 0.5) +
  geom_ribbon(aes(x = selribx, ymin = selriby,ymax = serriby, linetype = NA), alpha=0.1) +
  xlab("") +
  ylab("") 
ggp1 = ggp + 
  #ggtitle("all species") +
  theme(plot.title = element_text(hjust = 0.5, size = 10)) +
  theme(axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.title.y = element_blank(), axis.text.y = element_text(size = 9)) +
  theme(legend.title = element_text(size = 0, face = "bold"), legend.text = element_text(size = 8))+
  #theme(strip.background = element_rect(colour=NULL, fill=NA)) +
  theme(strip.text.x = element_text(size = 12, face = "bold")) +
  scale_size(guide = 'none') +
  scale_x_continuous(limits = c(1,300)) +
  scale_color_manual(values = c("#56B4E9","#D55E00","#009E73","#CC79A7"),
                     name="",
                     breaks=c("1","6","5","7"),
                     labels=c("control","insecticide","fungicide","combined")) +
  scale_fill_manual(values = c("#56B4E9","#D55E00","#009E73","#CC79A7"),
                    name="",
                    breaks=c("1","6","5","7"),
                    labels=c("control","insecticide","fungicide","combined"))




##################### plotting - SR ######################



temp2$pred = predict(fit9b, type = "response", re.form = NA, allow.new.levels=TRUE)

a = predict(fit9b, type = "response", re.form = NA)
b = predict(fit9b, type = "response")
c = b - a
temp2$newproportion.mortality = temp2$proportion.mortality - c
temp2[temp2$newproportion.mortality > 1,]$newproportion.mortality = 1
temp2[temp2$newproportion.mortality < 0,]$newproportion.mortality = 0

temp2$predm = 0
temp2$sel = 0
temp2$ser = 0


ltemp = temp2

predFun = function(fit) {
  predict(fit,ltemp, re.form = NA, allow.new.levels=TRUE)
}

bb = bootMer(fit9b,nsim=100,FUN=predFun)

for (i in 1:length(temp2$proportion.mortality))
{
  temp2$predm[i] = binomial()$linkinv(median(bb$t[,i]))
  temp2$sel[i] = binomial()$linkinv(median(bb$t[,i]) - sd(bb$t[,i]))
  temp2$ser[i] = binomial()$linkinv(median(bb$t[,i]) + sd(bb$t[,i]))
}

ggp = ggplot(temp2, aes(x = census.start, y = predm, col = as.factor(plotx)))  +
  geom_point(size = 2) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F) +
  geom_smooth(aes(x = census.start, y = sel, col = as.factor(plotx)), method = "glm", method.args = list(family = "binomial"), se = F) +
  
  geom_smooth(aes(x = census.start, y = ser, col = as.factor(plotx)), method = "glm", method.args = list(family = "binomial"), se = F)

##### 1

selribx = ggplot_build(ggp)$data[[3]]$x[1:80]
selriby = ggplot_build(ggp)$data[[3]]$y[1:80]

serribx = ggplot_build(ggp)$data[[4]]$x[1:80]
serriby = ggplot_build(ggp)$data[[4]]$y[1:80]

srib = cbind(selribx,selriby,serriby)
srib = as.data.frame(srib)

srib = srib[sample(nrow(srib),length(temp2[temp2$treatment.control == 1,]$proportion.mortality),replace = T),]
temp2$selribx[temp2$treatment.control == 1] = srib$selribx
temp2$selriby[temp2$treatment.control == 1] = srib$selriby
temp2$serriby[temp2$treatment.control == 1] = srib$serriby

##### 2

selribx = ggplot_build(ggp)$data[[3]]$x[81:160]
selriby = ggplot_build(ggp)$data[[3]]$y[81:160]

serribx = ggplot_build(ggp)$data[[4]]$x[81:160]
serriby = ggplot_build(ggp)$data[[4]]$y[81:160]

srib = cbind(selribx,selriby,serriby)
srib = as.data.frame(srib)

srib = srib[sample(nrow(srib),length(temp2[temp2$plot == "5",]$proportion.mortality),replace = T),]
temp2$selribx[temp2$plot == "5"] = srib$selribx
temp2$selriby[temp2$plot == "5"] = srib$selriby
temp2$serriby[temp2$plot == "5"] = srib$serriby

##### 3

selribx = ggplot_build(ggp)$data[[3]]$x[161:240]
selriby = ggplot_build(ggp)$data[[3]]$y[161:240]

serribx = ggplot_build(ggp)$data[[4]]$x[161:240]
serriby = ggplot_build(ggp)$data[[4]]$y[161:240]

srib = cbind(selribx,selriby,serriby)
srib = as.data.frame(srib)

srib = srib[sample(nrow(srib),length(temp2[temp2$plot == "6",]$proportion.mortality),replace = T),]
temp2$selribx[temp2$plot == "6"] = srib$selribx
temp2$selriby[temp2$plot == "6"] = srib$selriby
temp2$serriby[temp2$plot == "6"] = srib$serriby

##### 4

selribx = ggplot_build(ggp)$data[[3]]$x[241:320]
selriby = ggplot_build(ggp)$data[[3]]$y[241:320]

serribx = ggplot_build(ggp)$data[[4]]$x[241:320]
serriby = ggplot_build(ggp)$data[[4]]$y[241:320]

srib = cbind(selribx,selriby,serriby)
srib = as.data.frame(srib)

srib = srib[sample(nrow(srib),length(temp2[temp2$plot == "7",]$proportion.mortality),replace = T),]
temp2$selribx[temp2$plot == "7"] = srib$selribx
temp2$selriby[temp2$plot == "7"] = srib$selriby
temp2$serriby[temp2$plot == "7"] = srib$serriby



ggp = ggplot(temp2, aes(x = census.start, y = predm, col = as.factor(plotx), fill = as.factor(plotx)))  +
  geom_point(aes(x = census.start, y = newproportion.mortality, col = as.factor(plotx)), size = 0.5) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, linewidth = 0.5) +
  geom_ribbon(aes(x = selribx, ymin = selriby,ymax = serriby, linetype = NA), alpha=0.1) +
  xlab("") +
  ylab(expression(paste(italic("Syzygium rubicundum"))))
ggp2 = ggp + 
  #ggtitle("Syzygium rubicundum") +
  theme(plot.title = element_text(hjust = 0.5, size = 10, face = 'italic')) +
  theme(axis.title.x = element_blank(), axis.text.x = element_text(size = 9),
        axis.title.y = element_blank(), axis.text.y = element_text(size = 9)) +
  theme(legend.title = element_text(size = 0, face = "bold"), legend.text = element_text(size = 8))+
  #theme(strip.background = element_rect(colour=NULL, fill=NA)) +
  theme(strip.text.x = element_text(size = 12, face = "bold")) +
  scale_size(guide = 'none') +
  scale_x_continuous(limits = c(1,300)) +
  scale_color_manual(values = c("#56B4E9","#D55E00","#009E73","#CC79A7"),
                     name="",
                     breaks=c("1","6","5","7"),
                     labels=c("control","insecticide","fungicide","combined")) +
  scale_fill_manual(values = c("#56B4E9","#D55E00","#009E73","#CC79A7"),
                    name="",
                    breaks=c("1","6","5","7"),
                    labels=c("control","insecticide","fungicide","combined"))





##################### plotting - SP ######################



temp3$pred = predict(fit9c, type = "response", re.form = NA, allow.new.levels=TRUE)

a = predict(fit9c, type = "response", re.form = NA)
b = predict(fit9c, type = "response")
c = b - a
temp3$newproportion.mortality = temp3$proportion.mortality - c
temp3[temp3$newproportion.mortality > 1,]$newproportion.mortality = 1
#temp3[temp3$newproportion.mortality < 0,]$newproportion.mortality = 0

temp3$predm = 0
temp3$sel = 0
temp3$ser = 0


ltemp = temp3

predFun = function(fit) {
  predict(fit,ltemp, re.form = NA, allow.new.levels=TRUE)
}

bb = bootMer(fit9c,nsim=100,FUN=predFun)

for (i in 1:length(temp3$proportion.mortality))
{
  temp3$predm[i] = binomial()$linkinv(median(bb$t[,i]))
  temp3$sel[i] = binomial()$linkinv(median(bb$t[,i]) - sd(bb$t[,i]))
  temp3$ser[i] = binomial()$linkinv(median(bb$t[,i]) + sd(bb$t[,i]))
}

ggp = ggplot(temp3, aes(x = census.start, y = predm, col = as.factor(plotx)))  +
  geom_point(size = 2) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F) +
  geom_smooth(aes(x = census.start, y = sel, col = as.factor(plotx)), method = "glm", method.args = list(family = "binomial"), se = F) +
  
  geom_smooth(aes(x = census.start, y = ser, col = as.factor(plotx)), method = "glm", method.args = list(family = "binomial"), se = F)

##### 1

selribx = ggplot_build(ggp)$data[[3]]$x[1:80]
selriby = ggplot_build(ggp)$data[[3]]$y[1:80]

serribx = ggplot_build(ggp)$data[[4]]$x[1:80]
serriby = ggplot_build(ggp)$data[[4]]$y[1:80]

srib = cbind(selribx,selriby,serriby)
srib = as.data.frame(srib)

srib = srib[sample(nrow(srib),length(temp3[temp3$treatment.control == 1,]$proportion.mortality),replace = T),]
temp3$selribx[temp3$treatment.control == 1] = srib$selribx
temp3$selriby[temp3$treatment.control == 1] = srib$selriby
temp3$serriby[temp3$treatment.control == 1] = srib$serriby

##### 2

selribx = ggplot_build(ggp)$data[[3]]$x[81:160]
selriby = ggplot_build(ggp)$data[[3]]$y[81:160]

serribx = ggplot_build(ggp)$data[[4]]$x[81:160]
serriby = ggplot_build(ggp)$data[[4]]$y[81:160]

srib = cbind(selribx,selriby,serriby)
srib = as.data.frame(srib)

srib = srib[sample(nrow(srib),length(temp3[temp3$plot == "5",]$proportion.mortality),replace = T),]
temp3$selribx[temp3$plot == "5"] = srib$selribx
temp3$selriby[temp3$plot == "5"] = srib$selriby
temp3$serriby[temp3$plot == "5"] = srib$serriby

##### 3

selribx = ggplot_build(ggp)$data[[3]]$x[161:240]
selriby = ggplot_build(ggp)$data[[3]]$y[161:240]

serribx = ggplot_build(ggp)$data[[4]]$x[161:240]
serriby = ggplot_build(ggp)$data[[4]]$y[161:240]

srib = cbind(selribx,selriby,serriby)
srib = as.data.frame(srib)

srib = srib[sample(nrow(srib),length(temp3[temp3$plot == "6",]$proportion.mortality),replace = T),]
temp3$selribx[temp3$plot == "6"] = srib$selribx
temp3$selriby[temp3$plot == "6"] = srib$selriby
temp3$serriby[temp3$plot == "6"] = srib$serriby

##### 4

selribx = ggplot_build(ggp)$data[[3]]$x[241:320]
selriby = ggplot_build(ggp)$data[[3]]$y[241:320]

serribx = ggplot_build(ggp)$data[[4]]$x[241:320]
serriby = ggplot_build(ggp)$data[[4]]$y[241:320]

srib = cbind(selribx,selriby,serriby)
srib = as.data.frame(srib)

srib = srib[sample(nrow(srib),length(temp3[temp3$plot == "7",]$proportion.mortality),replace = T),]
temp3$selribx[temp3$plot == "7"] = srib$selribx
temp3$selriby[temp3$plot == "7"] = srib$selriby
temp3$serriby[temp3$plot == "7"] = srib$serriby



ggp = ggplot(temp3, aes(x = census.start, y = predm, col = as.factor(plotx), fill = as.factor(plotx)))  +
  geom_point(aes(x = census.start, y = newproportion.mortality, col = as.factor(plotx)), size = 0.5) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, linewidth = 0.5) +
  geom_ribbon(aes(x = selribx, ymin = selriby,ymax = serriby, linetype = NA), alpha=0.1) +
  xlab("") +
  ylab("")
ggp3 = ggp + 
  #ggtitle("Spatholobus purpureus") +
  theme(plot.title = element_text(hjust = 0.5, size = 10, face = 'italic')) +
  theme(axis.title.x = element_blank(), axis.text.x = element_text(size = 9),
        axis.title.y = element_blank(), axis.text.y = element_text(size = 9)) +
  theme(legend.title = element_text(size = 0, face = "bold"), legend.text = element_text(size = 8))+
  #theme(strip.background = element_rect(colour=NULL, fill=NA)) +
  theme(strip.text.x = element_text(size = 12, face = "bold")) +
  scale_size(guide = 'none') +
  scale_x_continuous(limits = c(1,100)) +
  scale_color_manual(values = c("#56B4E9","#D55E00","#009E73","#CC79A7"),
                     name="",
                     breaks=c("1","6","5","7"),
                     labels=c("control","insecticide","fungicide","combined")) +
  scale_fill_manual(values = c("#56B4E9","#D55E00","#009E73","#CC79A7"),
                    name="",
                    breaks=c("1","6","5","7"),
                    labels=c("control","insecticide","fungicide","combined"))



##################### plotting - all other species ######################



temp6$pred = predict(fit9f, type = "response", re.form = NA, allow.new.levels=TRUE)

a = predict(fit9f, type = "response", re.form = NA)
b = predict(fit9f, type = "response")
c = b - a
temp6$newproportion.mortality = temp6$proportion.mortality - c
temp6[temp6$newproportion.mortality > 1,]$newproportion.mortality = 1
temp6[temp6$newproportion.mortality < 0,]$newproportion.mortality = 0

temp6$predm = 0
temp6$sel = 0
temp6$ser = 0


ltemp = temp6

predFun = function(fit) {
  predict(fit,ltemp, re.form = NA, allow.new.levels=TRUE)
}

bb = bootMer(fit9f,nsim=100,FUN=predFun)

for (i in 1:length(temp6$proportion.mortality))
{
  temp6$predm[i] = binomial()$linkinv(median(bb$t[,i]))
  temp6$sel[i] = binomial()$linkinv(median(bb$t[,i]) - sd(bb$t[,i]))
  temp6$ser[i] = binomial()$linkinv(median(bb$t[,i]) + sd(bb$t[,i]))
}

ggp = ggplot(temp6, aes(x = census.start, y = predm, col = as.factor(plotx)))  +
  geom_point(size = 2) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F) +
  geom_smooth(aes(x = census.start, y = sel, col = as.factor(plotx)), method = "glm", method.args = list(family = "binomial"), se = F) +
  
  geom_smooth(aes(x = census.start, y = ser, col = as.factor(plotx)), method = "glm", method.args = list(family = "binomial"), se = F)

##### 1

selribx = ggplot_build(ggp)$data[[3]]$x[1:80]
selriby = ggplot_build(ggp)$data[[3]]$y[1:80]

serribx = ggplot_build(ggp)$data[[4]]$x[1:80]
serriby = ggplot_build(ggp)$data[[4]]$y[1:80]

srib = cbind(selribx,selriby,serriby)
srib = as.data.frame(srib)

srib = srib[sample(nrow(srib),length(temp6[temp6$treatment.control == 1,]$proportion.mortality),replace = T),]
temp6$selribx[temp6$treatment.control == 1] = srib$selribx
temp6$selriby[temp6$treatment.control == 1] = srib$selriby
temp6$serriby[temp6$treatment.control == 1] = srib$serriby

##### 2

selribx = ggplot_build(ggp)$data[[3]]$x[81:160]
selriby = ggplot_build(ggp)$data[[3]]$y[81:160]

serribx = ggplot_build(ggp)$data[[4]]$x[81:160]
serriby = ggplot_build(ggp)$data[[4]]$y[81:160]

srib = cbind(selribx,selriby,serriby)
srib = as.data.frame(srib)

srib = srib[sample(nrow(srib),length(temp6[temp6$plot == "5",]$proportion.mortality),replace = T),]
temp6$selribx[temp6$plot == "5"] = srib$selribx
temp6$selriby[temp6$plot == "5"] = srib$selriby
temp6$serriby[temp6$plot == "5"] = srib$serriby

##### 3

selribx = ggplot_build(ggp)$data[[3]]$x[161:240]
selriby = ggplot_build(ggp)$data[[3]]$y[161:240]

serribx = ggplot_build(ggp)$data[[4]]$x[161:240]
serriby = ggplot_build(ggp)$data[[4]]$y[161:240]

srib = cbind(selribx,selriby,serriby)
srib = as.data.frame(srib)

srib = srib[sample(nrow(srib),length(temp6[temp6$plot == "6",]$proportion.mortality),replace = T),]
temp6$selribx[temp6$plot == "6"] = srib$selribx
temp6$selriby[temp6$plot == "6"] = srib$selriby
temp6$serriby[temp6$plot == "6"] = srib$serriby

##### 4

selribx = ggplot_build(ggp)$data[[3]]$x[241:320]
selriby = ggplot_build(ggp)$data[[3]]$y[241:320]

serribx = ggplot_build(ggp)$data[[4]]$x[241:320]
serriby = ggplot_build(ggp)$data[[4]]$y[241:320]

srib = cbind(selribx,selriby,serriby)
srib = as.data.frame(srib)

srib = srib[sample(nrow(srib),length(temp6[temp6$plot == "7",]$proportion.mortality),replace = T),]
temp6$selribx[temp6$plot == "7"] = srib$selribx
temp6$selriby[temp6$plot == "7"] = srib$selriby
temp6$serriby[temp6$plot == "7"] = srib$serriby



ggp = ggplot(temp6, aes(x = census.start, y = predm, col = as.factor(plotx), fill = as.factor(plotx)))  +
  geom_point(aes(x = census.start, y = newproportion.mortality, col = as.factor(plotx)), size = 0.5) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, linewidth = 0.5) +
  geom_ribbon(aes(x = selribx, ymin = selriby,ymax = serriby, linetype = NA), alpha=0.1) +
  xlab("conspecific density (per square-meter)") 
ggp4 = ggp + 
  #ggtitle("all other species") +
  theme(plot.title = element_text(hjust = 0.5, size = 10)) +
  theme(axis.title.x = element_text(vjust = -2, size = 12), axis.text.x = element_text(size = 9),
        axis.title.y = element_blank(), axis.text.y = element_text(size = 9)) +
  theme(legend.title = element_text(size = 0, face = "bold"), legend.text = element_text(size = 8))+
  #theme(strip.background = element_rect(colour=NULL, fill=NA)) +
  theme(strip.text.x = element_text(size = 12, face = "bold")) +
  scale_size(guide = 'none') +
  scale_x_continuous(limits = c(1,50)) +
  scale_color_manual(values = c("#56B4E9","#D55E00","#009E73","#CC79A7"),
                     name="",
                     breaks=c("1","6","5","7"),
                     labels=c("control","insecticide","fungicide","combined")) +
  scale_fill_manual(values = c("#56B4E9","#D55E00","#009E73","#CC79A7"),
                    name="",
                    breaks=c("1","6","5","7"),
                    labels=c("control","insecticide","fungicide","combined"))




############################


library(gridExtra)
library(grid)

grid_arrange_shared_legend1 <- function(...) {
  plots <- list(...)
  g <- ggplotGrob(plots[[1]] + theme(legend.position="bottom"))$grobs
  legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
  lheight <- sum(legend$height)
  grid.arrange(top = textGrob("all species", rot=0, vjust = 1,
                              gp = gpar(fontfamily = "serif", fontsize = 10, col = 'black')),
               do.call(arrangeGrob, c(lapply(plots, function(x)
                 x + theme(legend.position="none")), list(nrow = 1))),
               ncol = 1,
               heights = unit.c(unit(0.895, "npc") - lheight, lheight))
}

grid_arrange_shared_legend2 <- function(...) {
  plots <- list(...)
  g <- ggplotGrob(plots[[1]] + theme(legend.position="bottom"))$grobs
  legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
  lheight <- sum(legend$height)
  grid.arrange(top = textGrob(expression(paste(italic("Syzygium rubicundum"))), rot=0, vjust = 0,
                              gp = gpar(fontfamily = "serif", fontsize = 10, col = 'black')),
               do.call(arrangeGrob, c(lapply(plots, function(x)
                 x + theme(legend.position="none")), list(nrow = 1))),
               ncol = 1,
               heights = unit.c(unit(0.895, "npc") - lheight, lheight))
}

grid_arrange_shared_legend3 <- function(...) {
  plots <- list(...)
  g <- ggplotGrob(plots[[1]] + theme(legend.position="bottom"))$grobs
  legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
  lheight <- sum(legend$height)
  grid.arrange(top = textGrob(expression(paste(italic("Spatholobus purpureus"))), rot=0, vjust = 0,
                              gp = gpar(fontfamily = "serif", fontsize = 10, col = 'black')),
               do.call(arrangeGrob, c(lapply(plots, function(x)
                 x + theme(legend.position="none")), list(nrow = 1))),
               ncol = 1,
               heights = unit.c(unit(0.895, "npc") - lheight, lheight))
}

grid_arrange_shared_legend4 <- function(...) {
  plots <- list(...)
  g <- ggplotGrob(plots[[1]] + theme(legend.position="bottom"))$grobs
  legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
  lheight <- sum(legend$height)
  grid.arrange(top = textGrob("all other species", rot=0, vjust = 1,
                              gp = gpar(fontfamily = "serif", fontsize = 10, col = 'black')),
               do.call(arrangeGrob, c(lapply(plots, function(x)
                 x + theme(legend.position="none")), list(nrow = 1))),
               legend,
               ncol = 1,
               heights = unit.c(unit(0.895, "npc") - lheight, lheight))
}

p1 = grid_arrange_shared_legend2(ggp2)
p2 = grid_arrange_shared_legend3(ggp3)
p3 = grid_arrange_shared_legend4(ggp4)

#, bottom=grid::textGrob("conspecific density (per square-meter)") top=grid::textGrob("seedling mortality from germination to establishment",
g = gridExtra::arrangeGrob(p1,p2,p3,nrow=3,ncol=1, 
                            left=grid::textGrob("probability of mortality - germination to establishment", rot=90, gp = gpar(fontfamily = "serif", fontsize = 12, col = 'black'))) ; 
  #grid::grid.newpage() ; 

jpeg('density_dependence.jpg', units="in", width=5, height=7, res=1000)
grid::grid.draw(g)
dev.off()










################ For presentation FUNGI ###################

## empty SR with only fungi

ggpw = ggplot(temp2[temp2$treatment.insecticide != 1,], aes(x = census.start, y = predm, col = as.factor(plotx), fill = as.factor(plotx)))  +
  #geom_point(aes(x = census.start, y = newproportion.mortality, col = as.factor(plotx)), size = 0.5) +
  #geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, linewidth = 0.5) +
  #geom_ribbon(aes(x = selribx, ymin = selriby,ymax = serriby, linetype = NA), alpha=0.1) +
  xlab(expression(paste(conspecific~density~"/"~m^2))) +
  ylab("per-capita mortality")


ggpw1 = ggpw + 
  ggtitle("Syzygium rubicundum") +
  theme(plot.title = element_text(hjust = 0.5, size = 10, face = 'italic')) +
  theme(axis.title.x = element_text(vjust = -2, size = 12), axis.text.x = element_text(size = 9),
        axis.title.y = element_text(vjust = 1, angle = 90, size = 12), axis.text.y = element_text(size = 9)) +
  theme(legend.title = element_text(size = 0, face = "bold"), legend.text = element_text(size = 8))+
  #theme(strip.background = element_rect(colour=NULL, fill=NA)) +
  theme(strip.text.x = element_text(size = 12, face = "bold")) +
  scale_size(guide = 'none') +
  scale_x_continuous(limits = c(1,300)) +
  scale_y_continuous(limits = c(0,1), breaks = c(0,0.2,0.4,0.6,0.8,1)) +
  scale_color_manual(values = c("#56B4E9","#D55E00","#009E73","#CC79A7"),
                     name="",
                     breaks=c("1","6","5","7"),
                     labels=c("control","insecticide","fungicide","combined")) +
  scale_fill_manual(values = c("#56B4E9","#D55E00","#009E73","#CC79A7"),
                    name="",
                    breaks=c("1","6","5","7"),
                    labels=c("control","insecticide","fungicide","combined"))

ggp = ggplot(temp2[temp2$treatment.insecticide != 1,], aes(x = census.start, y = predm, col = as.factor(plotx), fill = as.factor(plotx)))  +
  geom_point(aes(x = census.start, y = newproportion.mortality, col = as.factor(plotx)), size = 0.5) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, linewidth = 0.5) +
  geom_ribbon(aes(x = selribx, ymin = selriby,ymax = serriby, linetype = NA), alpha=0.1) +
  xlab(expression(paste(conspecific~density~"/"~m^2))) +
  ylab("per-capita mortality")


ggp1 = ggp + 
  ggtitle("Syzygium rubicundum") +
  theme(plot.title = element_text(hjust = 0.5, size = 10, face = 'italic')) +
  theme(axis.title.x = element_text(vjust = -2, size = 12), axis.text.x = element_text(size = 9),
        axis.title.y = element_text(vjust = 1, angle = 90, size = 12), axis.text.y = element_text(size = 9)) +
  theme(legend.title = element_text(size = 0, face = "bold"), legend.text = element_text(size = 8))+
  #theme(strip.background = element_rect(colour=NULL, fill=NA)) +
  theme(strip.text.x = element_text(size = 12, face = "bold")) +
  scale_size(guide = 'none') +
  scale_x_continuous(limits = c(1,300)) +
  scale_y_continuous(limits = c(0,1), breaks = c(0,0.2,0.4,0.6,0.8,1)) +
  scale_color_manual(values = c("#56B4E9","#D55E00","#009E73","#CC79A7"),
                     name="",
                     breaks=c("1","6","5","7"),
                     labels=c("control","insecticide","fungicide","combined")) +
  scale_fill_manual(values = c("#56B4E9","#D55E00","#009E73","#CC79A7"),
                    name="",
                    breaks=c("1","6","5","7"),
                    labels=c("control","insecticide","fungicide","combined"))

grid_arrange_shared_legend <- function(...) {
  plots <- list(...)
  g <- ggplotGrob(plots[[1]] + theme(legend.position="bottom"))$grobs
  legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
  lheight <- sum(legend$height)
  grid.arrange(
    do.call(arrangeGrob, c(lapply(plots[2], function(x)
      x + theme(legend.position="none")), list(nrow = 1))),
    legend,
    ncol = 1,
    heights = unit.c(unit(1, "npc") - lheight, lheight))
}

p = grid_arrange_shared_legend(ggp1,ggpw1)

#, bottom=grid::textGrob("conspecific density (per square-meter)") top=grid::textGrob("seedling mortality from germination to establishment",
#g = gridExtra::arrangeGrob(p,ncol=1) ; 
#grid::grid.newpage() ; 

tiff('C:/Users/ashwinv/Desktop/a.tiff', units="in", width=8, height=6, res=1000)
grid_arrange_shared_legend(ggp1,ggpw1)
dev.off()



## only control

ggpw = ggplot(temp2[temp2$treatment.control == 1,], aes(x = census.start, y = predm, col = as.factor(plotx), fill = as.factor(plotx)))  +
  geom_point(aes(x = census.start, y = newproportion.mortality, col = as.factor(plotx)), size = 0.5) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, linewidth = 0.5) +
  geom_ribbon(aes(x = selribx, ymin = selriby,ymax = serriby, linetype = NA), alpha=0.1) +
  xlab(expression(paste(conspecific~density~"/"~m^2))) +
  ylab("per-capita mortality")


ggpw1 = ggpw + 
  ggtitle("Syzygium rubicundum") +
  theme(plot.title = element_text(hjust = 0.5, size = 10, face = 'italic')) +
  theme(axis.title.x = element_text(vjust = -2, size = 12), axis.text.x = element_text(size = 9),
        axis.title.y = element_text(vjust = 1, angle = 90, size = 12), axis.text.y = element_text(size = 9)) +
  theme(legend.title = element_text(size = 0, face = "bold"), legend.text = element_text(size = 8))+
  #theme(strip.background = element_rect(colour=NULL, fill=NA)) +
  theme(strip.text.x = element_text(size = 12, face = "bold")) +
  scale_size(guide = 'none') +
  scale_x_continuous(limits = c(1,300)) +
  scale_y_continuous(limits = c(0,1), breaks = c(0,0.2,0.4,0.6,0.8,1)) +
  scale_color_manual(values = c("#56B4E9","#D55E00","#009E73","#CC79A7"),
                     name="",
                     breaks=c("1","6","5","7"),
                     labels=c("control","insecticide","fungicide","combined")) +
  scale_fill_manual(values = c("#56B4E9","#D55E00","#009E73","#CC79A7"),
                    name="",
                    breaks=c("1","6","5","7"),
                    labels=c("control","insecticide","fungicide","combined"))

ggp = ggplot(temp2[temp2$plotx != "7",], aes(x = census.start, y = predm, col = as.factor(plotx), fill = as.factor(plotx)))  +
  geom_point(aes(x = census.start, y = newproportion.mortality, col = as.factor(plotx)), size = 0.5) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, linewidth = 0.5) +
  geom_ribbon(aes(x = selribx, ymin = selriby,ymax = serriby, linetype = NA), alpha=0.1) +
  xlab(expression(paste(conspecific~density~"/"~m^2))) +
  ylab("per-capita mortality")


ggp1 = ggp + 
  ggtitle("Syzygium rubicundum") +
  theme(plot.title = element_text(hjust = 0.5, size = 10, face = 'italic')) +
  theme(axis.title.x = element_text(vjust = -2, size = 12), axis.text.x = element_text(size = 9),
        axis.title.y = element_text(vjust = 1, angle = 90, size = 12), axis.text.y = element_text(size = 9)) +
  theme(legend.title = element_text(size = 0, face = "bold"), legend.text = element_text(size = 8))+
  #theme(strip.background = element_rect(colour=NULL, fill=NA)) +
  theme(strip.text.x = element_text(size = 12, face = "bold")) +
  scale_size(guide = 'none') +
  scale_x_continuous(limits = c(1,300)) +
  scale_y_continuous(limits = c(0,1), breaks = c(0,0.2,0.4,0.6,0.8,1)) +
  scale_color_manual(values = c("#56B4E9","#D55E00","#009E73","#CC79A7"),
                     name="",
                     breaks=c("1","6","5","7"),
                     labels=c("control","insecticide","fungicide","combined")) +
  scale_fill_manual(values = c("#56B4E9","#D55E00","#009E73","#CC79A7"),
                    name="",
                    breaks=c("1","6","5","7"),
                    labels=c("control","insecticide","fungicide","combined"))

grid_arrange_shared_legend <- function(...) {
  plots <- list(...)
  g <- ggplotGrob(plots[[1]] + theme(legend.position="bottom"))$grobs
  legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
  lheight <- sum(legend$height)
  grid.arrange(
    do.call(arrangeGrob, c(lapply(plots[2], function(x)
      x + theme(legend.position="none")), list(nrow = 1))),
    legend,
    ncol = 1,
    heights = unit.c(unit(1, "npc") - lheight, lheight))
}

p = grid_arrange_shared_legend(ggp1,ggpw1)

#, bottom=grid::textGrob("conspecific density (per square-meter)") top=grid::textGrob("seedling mortality from germination to establishment",
#g = gridExtra::arrangeGrob(p,ncol=1) ; 
#grid::grid.newpage() ; 

tiff('C:/Users/ashwinv/Desktop/a.tiff', units="in", width=8, height=6, res=1000)
grid_arrange_shared_legend(ggp1,ggpw1)
dev.off()




## control and fungicide

ggpw = ggplot(temp2[temp2$treatment.insecticide != 1,], aes(x = census.start, y = predm, col = as.factor(plotx), fill = as.factor(plotx)))  +
  geom_point(aes(x = census.start, y = newproportion.mortality, col = as.factor(plotx)), size = 0.5) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, linewidth = 0.5) +
  geom_ribbon(aes(x = selribx, ymin = selriby,ymax = serriby, linetype = NA), alpha=0.1) +
  xlab(expression(paste(conspecific~density~"/"~m^2))) +
  ylab("per-capita mortality")


ggpw1 = ggpw + 
  ggtitle("Syzygium rubicundum") +
  theme(plot.title = element_text(hjust = 0.5, size = 10, face = 'italic')) +
  theme(axis.title.x = element_text(vjust = -2, size = 12), axis.text.x = element_text(size = 9),
        axis.title.y = element_text(vjust = 1, angle = 90, size = 12), axis.text.y = element_text(size = 9)) +
  theme(legend.title = element_text(size = 0, face = "bold"), legend.text = element_text(size = 8))+
  #theme(strip.background = element_rect(colour=NULL, fill=NA)) +
  theme(strip.text.x = element_text(size = 12, face = "bold")) +
  scale_size(guide = 'none') +
  scale_x_continuous(limits = c(1,300)) +
  scale_y_continuous(limits = c(0,1), breaks = c(0,0.2,0.4,0.6,0.8,1)) +
  scale_color_manual(values = c("#56B4E9","#D55E00","#009E73","#CC79A7"),
                     name="",
                     breaks=c("1","6","5","7"),
                     labels=c("control","insecticide","fungicide","combined")) +
  scale_fill_manual(values = c("#56B4E9","#D55E00","#009E73","#CC79A7"),
                    name="",
                    breaks=c("1","6","5","7"),
                    labels=c("control","insecticide","fungicide","combined"))

ggp = ggplot(temp2[temp2$plotx != "7",], aes(x = census.start, y = predm, col = as.factor(plotx), fill = as.factor(plotx)))  +
  geom_point(aes(x = census.start, y = newproportion.mortality, col = as.factor(plotx)), size = 0.5) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, linewidth = 0.5) +
  geom_ribbon(aes(x = selribx, ymin = selriby,ymax = serriby, linetype = NA), alpha=0.1) +
  xlab(expression(paste(conspecific~density~"/"~m^2))) +
  ylab("per-capita mortality")


ggp1 = ggp + 
  ggtitle("Syzygium rubicundum") +
  theme(plot.title = element_text(hjust = 0.5, size = 10, face = 'italic')) +
  theme(axis.title.x = element_text(vjust = -2, size = 12), axis.text.x = element_text(size = 9),
        axis.title.y = element_text(vjust = 1, angle = 90, size = 12), axis.text.y = element_text(size = 9)) +
  theme(legend.title = element_text(size = 0, face = "bold"), legend.text = element_text(size = 8))+
  #theme(strip.background = element_rect(colour=NULL, fill=NA)) +
  theme(strip.text.x = element_text(size = 12, face = "bold")) +
  scale_size(guide = 'none') +
  scale_x_continuous(limits = c(1,300)) +
  scale_y_continuous(limits = c(0,1), breaks = c(0,0.2,0.4,0.6,0.8,1)) +
  scale_color_manual(values = c("#56B4E9","#D55E00","#009E73","#CC79A7"),
                     name="",
                     breaks=c("1","6","5","7"),
                     labels=c("control","insecticide","fungicide","combined")) +
  scale_fill_manual(values = c("#56B4E9","#D55E00","#009E73","#CC79A7"),
                    name="",
                    breaks=c("1","6","5","7"),
                    labels=c("control","insecticide","fungicide","combined"))

grid_arrange_shared_legend <- function(...) {
  plots <- list(...)
  g <- ggplotGrob(plots[[1]] + theme(legend.position="bottom"))$grobs
  legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
  lheight <- sum(legend$height)
  grid.arrange(
    do.call(arrangeGrob, c(lapply(plots[2], function(x)
      x + theme(legend.position="none")), list(nrow = 1))),
    legend,
    ncol = 1,
    heights = unit.c(unit(1, "npc") - lheight, lheight))
}

p = grid_arrange_shared_legend(ggp1,ggpw1)

#, bottom=grid::textGrob("conspecific density (per square-meter)") top=grid::textGrob("seedling mortality from germination to establishment",
#g = gridExtra::arrangeGrob(p,ncol=1) ; 
#grid::grid.newpage() ; 

tiff('C:/Users/ashwinv/Desktop/a.tiff', units="in", width=8, height=6, res=1000)
grid_arrange_shared_legend(ggp1,ggpw1)
dev.off()



## control and fungicide and insecticide

ggpw = ggplot(temp2[temp2$plotx != "7",], aes(x = census.start, y = predm, col = as.factor(plotx), fill = as.factor(plotx)))  +
  geom_point(aes(x = census.start, y = newproportion.mortality, col = as.factor(plotx)), size = 0.5) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, linewidth = 0.5) +
  geom_ribbon(aes(x = selribx, ymin = selriby,ymax = serriby, linetype = NA), alpha=0.1) +
  xlab(expression(paste(conspecific~density~"/"~m^2))) +
  ylab("per-capita mortality")


ggpw1 = ggpw + 
  ggtitle("Syzygium rubicundum") +
  theme(plot.title = element_text(hjust = 0.5, size = 10, face = 'italic')) +
  theme(axis.title.x = element_text(vjust = -2, size = 12), axis.text.x = element_text(size = 9),
        axis.title.y = element_text(vjust = 1, angle = 90, size = 12), axis.text.y = element_text(size = 9)) +
  theme(legend.title = element_text(size = 0, face = "bold"), legend.text = element_text(size = 8))+
  #theme(strip.background = element_rect(colour=NULL, fill=NA)) +
  theme(strip.text.x = element_text(size = 12, face = "bold")) +
  scale_size(guide = 'none') +
  scale_x_continuous(limits = c(1,300)) +
  scale_y_continuous(limits = c(0,1), breaks = c(0,0.2,0.4,0.6,0.8,1)) +
  scale_color_manual(values = c("#56B4E9","#D55E00","#009E73","#CC79A7"),
                     name="",
                     breaks=c("1","6","5","7"),
                     labels=c("control","insecticide","fungicide","combined")) +
  scale_fill_manual(values = c("#56B4E9","#D55E00","#009E73","#CC79A7"),
                    name="",
                    breaks=c("1","6","5","7"),
                    labels=c("control","insecticide","fungicide","combined"))

ggp = ggplot(temp2[temp2$plotx != "7",], aes(x = census.start, y = predm, col = as.factor(plotx), fill = as.factor(plotx)))  +
  geom_point(aes(x = census.start, y = newproportion.mortality, col = as.factor(plotx)), size = 0.5) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, linewidth = 0.5) +
  geom_ribbon(aes(x = selribx, ymin = selriby,ymax = serriby, linetype = NA), alpha=0.1) +
  xlab(expression(paste(conspecific~density~"/"~m^2))) +
  ylab("per-capita mortality")


ggp1 = ggp + 
  ggtitle("Syzygium rubicundum") +
  theme(plot.title = element_text(hjust = 0.5, size = 10, face = 'italic')) +
  theme(axis.title.x = element_text(vjust = -2, size = 12), axis.text.x = element_text(size = 9),
        axis.title.y = element_text(vjust = 1, angle = 90, size = 12), axis.text.y = element_text(size = 9)) +
  theme(legend.title = element_text(size = 0, face = "bold"), legend.text = element_text(size = 8))+
  #theme(strip.background = element_rect(colour=NULL, fill=NA)) +
  theme(strip.text.x = element_text(size = 12, face = "bold")) +
  scale_size(guide = 'none') +
  scale_x_continuous(limits = c(1,300)) +
  scale_y_continuous(limits = c(0,1), breaks = c(0,0.2,0.4,0.6,0.8,1)) +
  scale_color_manual(values = c("#56B4E9","#D55E00","#009E73","#CC79A7"),
                     name="",
                     breaks=c("1","6","5","7"),
                     labels=c("control","insecticide","fungicide","combined")) +
  scale_fill_manual(values = c("#56B4E9","#D55E00","#009E73","#CC79A7"),
                    name="",
                    breaks=c("1","6","5","7"),
                    labels=c("control","insecticide","fungicide","combined"))

grid_arrange_shared_legend <- function(...) {
  plots <- list(...)
  g <- ggplotGrob(plots[[1]] + theme(legend.position="bottom"))$grobs
  legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
  lheight <- sum(legend$height)
  grid.arrange(
    do.call(arrangeGrob, c(lapply(plots[2], function(x)
      x + theme(legend.position="none")), list(nrow = 1))),
    legend,
    ncol = 1,
    heights = unit.c(unit(1, "npc") - lheight, lheight))
}

p = grid_arrange_shared_legend(ggp1,ggpw1)

#, bottom=grid::textGrob("conspecific density (per square-meter)") top=grid::textGrob("seedling mortality from germination to establishment",
#g = gridExtra::arrangeGrob(p,ncol=1) ; 
#grid::grid.newpage() ; 

tiff('C:/Users/ashwinv/Desktop/a.tiff', units="in", width=8, height=6, res=1000)
grid_arrange_shared_legend(ggp1,ggpw1)
dev.off()













################ For presentation INSECTS ###################

## empty SR with only insects

ggpw = ggplot(temp2[temp2$treatment.fungicide != 1,], aes(x = census.start, y = predm, col = as.factor(plotx), fill = as.factor(plotx)))  +
  #geom_point(aes(x = census.start, y = newproportion.mortality, col = as.factor(plotx)), size = 0.5) +
  #geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, linewidth = 0.5) +
  #geom_ribbon(aes(x = selribx, ymin = selriby,ymax = serriby, linetype = NA), alpha=0.1) +
  xlab(expression(paste(conspecific~density~"/"~m^2))) +
  ylab("per-capita mortality")


ggpw1 = ggpw + 
  ggtitle("Syzygium rubicundum") +
  theme(plot.title = element_text(hjust = 0.5, size = 10, face = 'italic')) +
  theme(axis.title.x = element_text(vjust = -2, size = 12), axis.text.x = element_text(size = 9),
        axis.title.y = element_text(vjust = 1, angle = 90, size = 12), axis.text.y = element_text(size = 9)) +
  theme(legend.title = element_text(size = 0, face = "bold"), legend.text = element_text(size = 8))+
  #theme(strip.background = element_rect(colour=NULL, fill=NA)) +
  theme(strip.text.x = element_text(size = 12, face = "bold")) +
  scale_size(guide = 'none') +
  scale_x_continuous(limits = c(1,200)) +
  scale_y_continuous(limits = c(0,1), breaks = c(0,0.2,0.4,0.6,0.8,1)) +
  scale_color_manual(values = c("#56B4E9","#009E73","#D55E00","#CC79A7"),
                     name="",
                     breaks=c("1","6","5","7"),
                     labels=c("control","insecticide","fungicide","combined")) +
  scale_fill_manual(values = c("#56B4E9","#009E73","#D55E00","#CC79A7"),
                    name="",
                    breaks=c("1","6","5","7"),
                    labels=c("control","insecticide","fungicide","combined"))

ggp = ggplot(temp2[temp2$treatment.fungicide != 1,], aes(x = census.start, y = predm, col = as.factor(plotx), fill = as.factor(plotx)))  +
  geom_point(aes(x = census.start, y = newproportion.mortality, col = as.factor(plotx)), size = 0.5) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, linewidth = 0.5) +
  geom_ribbon(aes(x = selribx, ymin = selriby,ymax = serriby, linetype = NA), alpha=0.1) +
  xlab(expression(paste(conspecific~density~"/"~m^2))) +
  ylab("per-capita mortality")


ggp1 = ggp + 
  ggtitle("Syzygium rubicundum") +
  theme(plot.title = element_text(hjust = 0.5, size = 10, face = 'italic')) +
  theme(axis.title.x = element_text(vjust = -2, size = 12), axis.text.x = element_text(size = 9),
        axis.title.y = element_text(vjust = 1, angle = 90, size = 12), axis.text.y = element_text(size = 9)) +
  theme(legend.title = element_text(size = 0, face = "bold"), legend.text = element_text(size = 8))+
  #theme(strip.background = element_rect(colour=NULL, fill=NA)) +
  theme(strip.text.x = element_text(size = 12, face = "bold")) +
  scale_size(guide = 'none') +
  scale_x_continuous(limits = c(1,200)) +
  scale_y_continuous(limits = c(0,1), breaks = c(0,0.2,0.4,0.6,0.8,1)) +
  scale_color_manual(values = c("#56B4E9","#009E73","#D55E00","#CC79A7"),
                     name="",
                     breaks=c("1","6","5","7"),
                     labels=c("control","insecticide","fungicide","combined")) +
  scale_fill_manual(values = c("#56B4E9","#009E73","#D55E00","#CC79A7"),
                    name="",
                    breaks=c("1","6","5","7"),
                    labels=c("control","insecticide","fungicide","combined"))

grid_arrange_shared_legend <- function(...) {
  plots <- list(...)
  g <- ggplotGrob(plots[[1]] + theme(legend.position="bottom"))$grobs
  legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
  lheight <- sum(legend$height)
  grid.arrange(
    do.call(arrangeGrob, c(lapply(plots[2], function(x)
      x + theme(legend.position="none")), list(nrow = 1))),
    legend,
    ncol = 1,
    heights = unit.c(unit(1, "npc") - lheight, lheight))
}

p = grid_arrange_shared_legend(ggp1,ggpw1)

#, bottom=grid::textGrob("conspecific density (per square-meter)") top=grid::textGrob("seedling mortality from germination to establishment",
#g = gridExtra::arrangeGrob(p,ncol=1) ; 
#grid::grid.newpage() ; 

tiff('C:/Users/ashwinv/Desktop/a.tiff', units="in", width=8, height=6, res=1000)
grid_arrange_shared_legend(ggp1,ggpw1)
dev.off()



## only control

ggpw = ggplot(temp2[temp2$treatment.control == 1,], aes(x = census.start, y = predm, col = as.factor(plotx), fill = as.factor(plotx)))  +
  geom_point(aes(x = census.start, y = newproportion.mortality, col = as.factor(plotx)), size = 0.5) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, linewidth = 0.5) +
  geom_ribbon(aes(x = selribx, ymin = selriby,ymax = serriby, linetype = NA), alpha=0.1) +
  xlab(expression(paste(conspecific~density~"/"~m^2))) +
  ylab("per-capita mortality")


ggpw1 = ggpw + 
  ggtitle("Syzygium rubicundum") +
  theme(plot.title = element_text(hjust = 0.5, size = 10, face = 'italic')) +
  theme(axis.title.x = element_text(vjust = -2, size = 12), axis.text.x = element_text(size = 9),
        axis.title.y = element_text(vjust = 1, angle = 90, size = 12), axis.text.y = element_text(size = 9)) +
  theme(legend.title = element_text(size = 0, face = "bold"), legend.text = element_text(size = 8))+
  #theme(strip.background = element_rect(colour=NULL, fill=NA)) +
  theme(strip.text.x = element_text(size = 12, face = "bold")) +
  scale_size(guide = 'none') +
  scale_x_continuous(limits = c(1,200)) +
  scale_y_continuous(limits = c(0,1), breaks = c(0,0.2,0.4,0.6,0.8,1)) +
  scale_color_manual(values = c("#56B4E9","#009E73","#D55E00","#CC79A7"),
                     name="",
                     breaks=c("1","6","5","7"),
                     labels=c("control","insecticide","fungicide","combined")) +
  scale_fill_manual(values = c("#56B4E9","#009E73","#D55E00","#CC79A7"),
                    name="",
                    breaks=c("1","6","5","7"),
                    labels=c("control","insecticide","fungicide","combined"))

ggp = ggplot(temp2[temp2$treatment.fungicide != 1,], aes(x = census.start, y = predm, col = as.factor(plotx), fill = as.factor(plotx)))  +
  geom_point(aes(x = census.start, y = newproportion.mortality, col = as.factor(plotx)), size = 0.5) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, linewidth = 0.5) +
  geom_ribbon(aes(x = selribx, ymin = selriby,ymax = serriby, linetype = NA), alpha=0.1) +
  xlab(expression(paste(conspecific~density~"/"~m^2))) +
  ylab("per-capita mortality")


ggp1 = ggp + 
  ggtitle("Syzygium rubicundum") +
  theme(plot.title = element_text(hjust = 0.5, size = 10, face = 'italic')) +
  theme(axis.title.x = element_text(vjust = -2, size = 12), axis.text.x = element_text(size = 9),
        axis.title.y = element_text(vjust = 1, angle = 90, size = 12), axis.text.y = element_text(size = 9)) +
  theme(legend.title = element_text(size = 0, face = "bold"), legend.text = element_text(size = 8))+
  #theme(strip.background = element_rect(colour=NULL, fill=NA)) +
  theme(strip.text.x = element_text(size = 12, face = "bold")) +
  scale_size(guide = 'none') +
  scale_x_continuous(limits = c(1,200)) +
  scale_y_continuous(limits = c(0,1), breaks = c(0,0.2,0.4,0.6,0.8,1)) +
  scale_color_manual(values = c("#56B4E9","#009E73","#D55E00","#CC79A7"),
                     name="",
                     breaks=c("1","6","5","7"),
                     labels=c("control","insecticide","fungicide","combined")) +
  scale_fill_manual(values = c("#56B4E9","#009E73","#D55E00","#CC79A7"),
                    name="",
                    breaks=c("1","6","5","7"),
                    labels=c("control","insecticide","fungicide","combined"))

grid_arrange_shared_legend <- function(...) {
  plots <- list(...)
  g <- ggplotGrob(plots[[1]] + theme(legend.position="bottom"))$grobs
  legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
  lheight <- sum(legend$height)
  grid.arrange(
    do.call(arrangeGrob, c(lapply(plots[2], function(x)
      x + theme(legend.position="none")), list(nrow = 1))),
    legend,
    ncol = 1,
    heights = unit.c(unit(1, "npc") - lheight, lheight))
}

p = grid_arrange_shared_legend(ggp1,ggpw1)

#, bottom=grid::textGrob("conspecific density (per square-meter)") top=grid::textGrob("seedling mortality from germination to establishment",
#g = gridExtra::arrangeGrob(p,ncol=1) ; 
#grid::grid.newpage() ; 

tiff('C:/Users/ashwinv/Desktop/a.tiff', units="in", width=8, height=6, res=1000)
grid_arrange_shared_legend(ggp1,ggpw1)
dev.off()




## control and insecticide

ggpw = ggplot(temp2[temp2$treatment.fungicide != 1,], aes(x = census.start, y = predm, col = as.factor(plotx), fill = as.factor(plotx)))  +
  geom_point(aes(x = census.start, y = newproportion.mortality, col = as.factor(plotx)), size = 0.5) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, linewidth = 0.5) +
  geom_ribbon(aes(x = selribx, ymin = selriby,ymax = serriby, linetype = NA), alpha=0.1) +
  xlab(expression(paste(conspecific~density~"/"~m^2))) +
  ylab("per-capita mortality")


ggpw1 = ggpw + 
  ggtitle("Syzygium rubicundum") +
  theme(plot.title = element_text(hjust = 0.5, size = 10, face = 'italic')) +
  theme(axis.title.x = element_text(vjust = -2, size = 12), axis.text.x = element_text(size = 9),
        axis.title.y = element_text(vjust = 1, angle = 90, size = 12), axis.text.y = element_text(size = 9)) +
  theme(legend.title = element_text(size = 0, face = "bold"), legend.text = element_text(size = 8))+
  #theme(strip.background = element_rect(colour=NULL, fill=NA)) +
  theme(strip.text.x = element_text(size = 12, face = "bold")) +
  scale_size(guide = 'none') +
  scale_x_continuous(limits = c(1,200)) +
  scale_y_continuous(limits = c(0,1), breaks = c(0,0.2,0.4,0.6,0.8,1)) +
  scale_color_manual(values = c("#56B4E9","#009E73","#D55E00","#CC79A7"),
                     name="",
                     breaks=c("1","6","5","7"),
                     labels=c("control","insecticide","fungicide","combined")) +
  scale_fill_manual(values = c("#56B4E9","#009E73","#D55E00","#CC79A7"),
                    name="",
                    breaks=c("1","6","5","7"),
                    labels=c("control","insecticide","fungicide","combined"))

ggp = ggplot(temp2[temp2$treatment.fungicide != 1,], aes(x = census.start, y = predm, col = as.factor(plotx), fill = as.factor(plotx)))  +
  geom_point(aes(x = census.start, y = newproportion.mortality, col = as.factor(plotx)), size = 0.5) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, linewidth = 0.5) +
  geom_ribbon(aes(x = selribx, ymin = selriby,ymax = serriby, linetype = NA), alpha=0.1) +
  xlab(expression(paste(conspecific~density~"/"~m^2))) +
  ylab("per-capita mortality")


ggp1 = ggp + 
  ggtitle("Syzygium rubicundum") +
  theme(plot.title = element_text(hjust = 0.5, size = 10, face = 'italic')) +
  theme(axis.title.x = element_text(vjust = -2, size = 12), axis.text.x = element_text(size = 9),
        axis.title.y = element_text(vjust = 1, angle = 90, size = 12), axis.text.y = element_text(size = 9)) +
  theme(legend.title = element_text(size = 0, face = "bold"), legend.text = element_text(size = 8))+
  #theme(strip.background = element_rect(colour=NULL, fill=NA)) +
  theme(strip.text.x = element_text(size = 12, face = "bold")) +
  scale_size(guide = 'none') +
  scale_x_continuous(limits = c(1,200)) +
  scale_y_continuous(limits = c(0,1), breaks = c(0,0.2,0.4,0.6,0.8,1)) +
  scale_color_manual(values = c("#56B4E9","#009E73","#D55E00","#CC79A7"),
                     name="",
                     breaks=c("1","6","5","7"),
                     labels=c("control","insecticide","fungicide","combined")) +
  scale_fill_manual(values = c("#56B4E9","#009E73","#D55E00","#CC79A7"),
                    name="",
                    breaks=c("1","6","5","7"),
                    labels=c("control","insecticide","fungicide","combined"))

grid_arrange_shared_legend <- function(...) {
  plots <- list(...)
  g <- ggplotGrob(plots[[1]] + theme(legend.position="bottom"))$grobs
  legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
  lheight <- sum(legend$height)
  grid.arrange(
    do.call(arrangeGrob, c(lapply(plots[2], function(x)
      x + theme(legend.position="none")), list(nrow = 1))),
    legend,
    ncol = 1,
    heights = unit.c(unit(1, "npc") - lheight, lheight))
}

p = grid_arrange_shared_legend(ggp1,ggpw1)

#, bottom=grid::textGrob("conspecific density (per square-meter)") top=grid::textGrob("seedling mortality from germination to establishment",
#g = gridExtra::arrangeGrob(p,ncol=1) ; 
#grid::grid.newpage() ; 

tiff('C:/Users/ashwinv/Desktop/a.tiff', units="in", width=8, height=6, res=1000)
grid_arrange_shared_legend(ggp1,ggpw1)
dev.off()



########## Spatholobus #########



## control and fungicide and insecticide

ggpw = ggplot(temp3[temp3$plotx != "7",], aes(x = census.start, y = predm, col = as.factor(plotx), fill = as.factor(plotx)))  +
  geom_point(aes(x = census.start, y = newproportion.mortality, col = as.factor(plotx)), size = 0.5) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, linewidth = 0.5) +
  geom_ribbon(aes(x = selribx, ymin = selriby,ymax = serriby, linetype = NA), alpha=0.1) +
  xlab(expression(paste(conspecific~density~"/"~m^2))) +
  ylab("per-capita mortality")


ggpw1 = ggpw + 
  ggtitle("Spatholobus purpureus") +
  theme(plot.title = element_text(hjust = 0.5, size = 10, face = 'italic')) +
  theme(axis.title.x = element_text(vjust = -2, size = 12), axis.text.x = element_text(size = 9),
        axis.title.y = element_text(vjust = 1, angle = 90, size = 12), axis.text.y = element_text(size = 9)) +
  theme(legend.title = element_text(size = 0, face = "bold"), legend.text = element_text(size = 8))+
  #theme(strip.background = element_rect(colour=NULL, fill=NA)) +
  theme(strip.text.x = element_text(size = 12, face = "bold")) +
  scale_size(guide = 'none') +
  scale_x_continuous(limits = c(1,100)) +
  scale_y_continuous(limits = c(0,1), breaks = c(0,0.2,0.4,0.6,0.8,1)) +
  scale_color_manual(values = c("#56B4E9","#D55E00","#009E73","#CC79A7"),
                     name="",
                     breaks=c("1","6","5","7"),
                     labels=c("control","insecticide","fungicide","combined")) +
  scale_fill_manual(values = c("#56B4E9","#D55E00","#009E73","#CC79A7"),
                    name="",
                    breaks=c("1","6","5","7"),
                    labels=c("control","insecticide","fungicide","combined"))

ggp = ggplot(temp3[temp3$plotx != "7",], aes(x = census.start, y = predm, col = as.factor(plotx), fill = as.factor(plotx)))  +
  geom_point(aes(x = census.start, y = newproportion.mortality, col = as.factor(plotx)), size = 0.5) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, linewidth = 0.5) +
  geom_ribbon(aes(x = selribx, ymin = selriby,ymax = serriby, linetype = NA), alpha=0.1) +
  xlab(expression(paste(conspecific~density~"/"~m^2))) +
  ylab("per-capita mortality")


ggp1 = ggp + 
  ggtitle("Spatholobus purpureus") +
  theme(plot.title = element_text(hjust = 0.5, size = 10, face = 'italic')) +
  theme(axis.title.x = element_text(vjust = -2, size = 12), axis.text.x = element_text(size = 9),
        axis.title.y = element_text(vjust = 1, angle = 90, size = 12), axis.text.y = element_text(size = 9)) +
  theme(legend.title = element_text(size = 0, face = "bold"), legend.text = element_text(size = 8))+
  #theme(strip.background = element_rect(colour=NULL, fill=NA)) +
  theme(strip.text.x = element_text(size = 12, face = "bold")) +
  scale_size(guide = 'none') +
  scale_x_continuous(limits = c(1,100)) +
  scale_y_continuous(limits = c(0,1), breaks = c(0,0.2,0.4,0.6,0.8,1)) +
  scale_color_manual(values = c("#56B4E9","#D55E00","#009E73","#CC79A7"),
                     name="",
                     breaks=c("1","6","5","7"),
                     labels=c("control","insecticide","fungicide","combined")) +
  scale_fill_manual(values = c("#56B4E9","#D55E00","#009E73","#CC79A7"),
                    name="",
                    breaks=c("1","6","5","7"),
                    labels=c("control","insecticide","fungicide","combined"))

grid_arrange_shared_legend <- function(...) {
  plots <- list(...)
  g <- ggplotGrob(plots[[1]] + theme(legend.position="bottom"))$grobs
  legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
  lheight <- sum(legend$height)
  grid.arrange(
    do.call(arrangeGrob, c(lapply(plots[2], function(x)
      x + theme(legend.position="none")), list(nrow = 1))),
    legend,
    ncol = 1,
    heights = unit.c(unit(1, "npc") - lheight, lheight))
}

p = grid_arrange_shared_legend(ggp1,ggpw1)

#, bottom=grid::textGrob("conspecific density (per square-meter)") top=grid::textGrob("seedling mortality from germination to establishment",
#g = gridExtra::arrangeGrob(p,ncol=1) ; 
#grid::grid.newpage() ; 

tiff('C:/Users/ashwinv/Desktop/a.tiff', units="in", width=8, height=6, res=1000)
grid_arrange_shared_legend(ggp1,ggpw1)
dev.off()
```